Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-15 doc/reviews/ResponseToReviewer3.tex

In this work we used similar numerical techniques to solve the integral equations when some boundaries are quite close to each other.  As the repulsive Morse potential works well to prevent overlapping of particles (provided the time step size is sufficiently small), our previous results in Quaife, Veerapaneni and Young, 2019, Phys. Rev. Fluids gives us confidence in the accuracy of the fluid flow in the thin space between the particles.

\item Change: We added sentences to describe how the lubrication hydrodynamics in a narrow space between boundaries is well-captured within the boundary integral formulation in page 4, starting in line 129.

\end{itemize}

\noindent
\comment{{\bf 2.} Fig.~3 plots the time evolution of the reduced area in (a) and
the excess length of the bilayer structure in (b). Both show obvious
oscillations with multiple frequencies, which are not as smooth as the
inset of (c) showing one dominant frequency. The authors are suggested
to explain the source of multiple frequencies generated in the time
evolution of $A$ and $\Delta$.}
\begin{itemize}
  \item  Response: This part needs to be fixed with the FFT of the data that Rolf sent to Bryan.
  {\sl What follows is from Peter:
  Fig.~3(c) clearly shows that the total length of the JP vesicle has a steady periodic motion 
which is different from the trends shown in panels (a) and (b). We showed the actual time evolution of $A^*$ and $\Delta$ and fitting curves in (a). 
The idea is to show that we can use the fitting data to acquire the numerical expected teminal 
reduced area $A^*_\infty$. Therefore the multiple frequencies during simulations have no correlations between
the output in (c) and (d).}

\item Change:

\noindent
\comment{{\bf 3.} Fig.~6 illustrates the migration process of a JP vesicle in a
parabolic flow, where the moving velocity is 8 nm/ns and the time frame
is 0 to 12 $\mu$s. Given the length scale R = 20 nm, the migration
distance should be $1000 \times R$. However, in the figure, it shows a
migration distance about $4 \times R$. The authors are suggested to
double-check their model parameterization.}
\begin{itemize}
  \item Response: Fig.~6 shows snapshots for 4 time frames from 0 to 12 $\mu$s and the trajectory of the centriod is demonstrated. Therefore the dashed horizontal line of Fig.~6 represents time in units of $\mu$s and the vertical axis represents the scaled $y$ position of the centroid of the JP vesicle.
  \item Change: In the caption of Fig.~6 (page 14) we explain that the horizontal and vertical axes.

\noindent
\comment{{\bf 4.} In Fig.~10, the significant discontinuities in streamlines
across the surface of vesicles are observed, while in most other cases
the streamlines are smooth across the interface of vesicles. The authors
are suggested to describe such discontinuity and provide the
explanation.}
\begin{itemize}
  \item Response: We thank the Reviewer for pointing this out and this issue occurred due to a mistake made in post-processing
steps. Moreover, we do expect some  streamlines with large variation in gradient when they cross the JP vesicle interface.

\item Change: We corrected the original Fig.~10 by plotting all continuous streamlines. 
\end{itemize}

### 2022-02-15 doc/reviews/ResponseToReviewer1.tex

\section*{Response to Reviewer 1}
\noindent
\comment{Overall, the paper is original and interesting. The derivation
of the hydrophobic force without singular integrals is smart and well
written. The characterization of the effective properties of the
coarse-grained vesicles is also of interest and carefully conducted.
However, in many instances the manuscript looks more like a catalogue of
the different behaviors JP vesicles can exhibit in linear flows, rather
than a comprehensive study. The authors describe a few interesting
phenomena but only partially address the exciting physical questions
related to them. The paper lacks quantitative comparisons with continuum
models, parametric studies and detailed explanations to meet the
standards of JFM. In addition, the manuscript seems to have been written
in haste: a figure with no apparent connection to the content of the
paper has been inserted without being referenced or discussed in the
text (see below), some parts need some serious proofreading and
additional clarifications.}
\begin{itemize}
  \item {\bf Response to Summary}: 	We thank the Reviewer for the assessmnet of our manuscript submission. In response
to the comments, we have undertaken a major revision in including parametric studies and quantitative comparisons between models. We perforemed a number of simulations 
in studies of inter-monolayer friction coefficients and an additional numerical investigation 
of permeabilities. We have ensured that all figures are conneted with the corresponding content. 
  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
  \end{quotation}
\end{itemize}

\noindent
\comment{There is no parametric study of the effect of the particle size
on the effective properties of the vesicles (interlayer friction,
stretching modulus, permeability,etc$\ldots$). The authors defer this
part for future work in the conclusions, but since the effect of the
particle size is important, as evidenced in Section 4.3, it should be
explored and explained more thoroughly in the manuscript, otherwise the
research would be too incremental. The effect of particle shape seems
indeed more complex and out of the scope of the current paper.}
\begin{itemize}
  \item Response: This comment encouraged us to present more convergence studies in the choices of model parameters. We made a worthwhile effort to perform a large number of simulations. We agree with the Reviewer that the particle/vesicle shape is complex with the setup therefore we adopted small changes in particle sizes and reported all the results.
  \item Change: We revised Table 1 (page 12) and added Table 2 (page 16) to account for effective properties of vesicles with different size of particles. We added a short description of the new Table 1 in lines 354-359. 
\end{itemize}

\noindent
\comment{I understand that the results of Section 4.4 are mostly
qualitative and that the goal is to show the visual agreement between
the coarse-grained and continuum vesicle models, but it would be
insightful to provide quantitative comparisons to measure how close they
are to each other.}
\begin{itemize}
  \item Response: We agree with the Reviewer that we briefly illustrated the capability of simulating membrane rupture via the proposed model and numerical algorithm in the first submission of the manuscript. We further performed a series of study to find the critical shear rate for the appearance of membrane rupture and the correspnding movie is added as a supplementary material. We also included the description in the section of membrane rupture.
  \item Change: We added a short description of vesicle rupture (lines 374-376) in page 13. We added a movie of vesicle rupture (Movie S4) in the supplementary material (page 25).

@@

\noindent
\comment{I understand that the results of Section 4.4 are mostly
qualitative and that the goal is to show the visual agreement between
the coarse-grained and continuum vesicle models, but it would be
insightful to provide quantitative comparisons to measure how close they
are to each other.}
\begin{itemize}
  \item Response: We agree with the Reviewer that we briefly illustrated the capability of simulating membrane rupture via the proposed model and numerical algorithm in the first submission of the manuscript. We further performed a series of study to find the critical shear rate for the appearance of membrane rupture and the correspnding movie is added as a supplementary material. We also included the description in the section of membrane rupture.
  \item Change: We added a short description of vesicle rupture (lines 374-376) in page 13. We added a movie of vesicle rupture (Movie S4) in the supplementary material (page 25).

\end{itemize}

\noindent
\comment{The problem is not nondimensionalized with the characteristic
scales of the system but with ns, nm and $\text{pN} \cdot
\text{nm}^{-2}$. This (unusual) nondimensionalization makes it hard to
compare physical quantities and to define order parameters that would
explain/characterize some phenomena observed in the simulations
(e.g.~the membrane rupture).}

\begin{itemize}
  \item Response: We thank the Reviewer to point this out. There is a significant difference between 
the proposed model in the manuscript and other continuum models in literatures. For example, refer to \emph{Rahimian, et al., J. Comput. Phys., 2011}, the 
provided time scale is $\tau = \mu R_0^3/\kappa_B$ where $\mu$ the fluid viscosity and $\kappa_B$ the bending modulus. $R_0$ is the initial radius of the reference vesicle. Since the bending modulus results from the hydrophobic attraction between Janus particles and their dynamics in a viscous fluid in the proposed model, we thus scaled time with a realistic characteristic time ns. With the use of the detailed scaling laws described in section 4.1, we aim to have comparable
numerical results against the experiments. Moreover, if we attempt to calculate the characteristic 
time scale using characteristic length and energy scales, it will also result a value of order ns. 
Since the system involves multiple length scales, diameter of the particle $l_0$ and size of the JP
vesicle $R_0$, we decided to use ns to perform nondimensionalization for simplicity.

Finally we did manage to come up with an appropriate capillary number to characterize the rupture of a Janus vesicle under a linear shear flow at a high shear rate.

\item Change: Place where the critical capillary number is given and discussed.

\noindent
\comment{For the sake of clarity, at the end of Section 3 the authors
should summarize the exact set of equations they use and the unknowns
they solve for.}
\begin{itemize}
  \item Response: We followed the suggestion given by the Reviewer that a summary about what to solve throughout the entire algorithm is provided at the end of Section 3.
  \item Change: A short paragraph is added in page 8 (lines 248-253).
\end{itemize}

\noindent
\comment{General comment for all the figures with colormaps: it would be
good to use colorblind friendly colormaps for colorblind people and for
black and white printing.}
\begin{itemize}
  \item Response: We thank the Review for having this meaningful comment and we agree that changing all the figure 
to colorblind friendly colormap is insightful. We will make this change for all figures once the manuscript is accepted. All the new figures are made with colorblind friendly colormaps.

\item Change: All the modified figures (Figs.~ 9, 10, 11, 12,  13) are made with colorblind friendly colormaps. 
\end{itemize}

\noindent
\comment{Figure 1: the arc length $L$ does not appear in panel (c).}
\begin{itemize}
  \item Change: We deleted the sentence ``$L$ is the arc length''.
\end{itemize}

\noindent
\comment{Line 50: typo: ``well-known"}
\begin{itemize}
  \item Change: This typo is corrected.
\end{itemize}

\noindent
\comment{Page 3: the first two paragraphs seem to be a bit disconnected
from the rest of the introduction. Maybe the authors should rewrite that
part so that there is a transition from the physical problem into
consideration to the various numerical methods used in the literature to
simulate it.}
\begin{itemize}
 \item Response: We thank the referee for pointing this out. We deleted the disconnected paragraph that started with "Brandner...." and modified the end of the following paragraph in response to the next comment from the reviewer.
  \item Change: The paragraph ``Brandner {\it et al} (2019) used the coarsae-grained...." is removed.
\end{itemize}

\noindent
\comment{Line 70: ``we maintain contact-free suspensions with a
relatively weak non-stiff repulsive force". What do you mean by
relatively weak repulsive force ? Weak compared to what? (see additional
question on this hereinafter).}
\begin{itemize}
  \item Response: We modified this description for better clarity.
  \item Change: Page 3, lines 64-65, we changed ``relatively weak repulsive force" to ``relatively soft repulsive force" and added ``(compared to the short-range repulsion that diverges in the Lennard-Jones potential)".

\noindent
\comment{Equation (2.4) is not necessary as the no-slip boundary
condition is standard and it is redundant with (2.5).}
\begin{itemize}
  \item Change: We deleted the redundant equation (2.5) mentioned by the Reviewer.
\end{itemize}

@@

\end{itemize}

\noindent
\comment{Equation (2.4) is not necessary as the no-slip boundary
condition is standard and it is redundant with (2.5).}
\begin{itemize}
  \item Change: We deleted the redundant equation (2.5) mentioned by the Reviewer.
\end{itemize}

\noindent
\comment{Section 2.2: for clarity, define the variable u as the
hydrophobic attraction potential in the first paragraph.}

\noindent
\comment{The equations of the continuous time evolution of the particle
positions and orientations should be written in Section 2 to close the
problem.}
\begin{itemize}
  \item Response: Section 2.2 introduces the imposed forces and torques in hydrophobic attraction and repulsion that are not used to obtain particle directions directly. Following the next comment by 
the Reviewer, we agreed that Section 2.3 should be moved to the end of Section 3 and we complete the change.
\item Change: We moved Section 2.3 to the end of Section 3.
\end{itemize}

\noindent
\comment{I think the time-discretization Section 2.3 should go at the
end of Section 3 since this is the one devoted to the numerical
discretization of the governing equations. Also, the sentence ``particle
collisions are avoided even when using a relatively large time step" is
very vague.  What do you mean by ``relatively large time step"? Compared
to what time scale?}
\begin{itemize}
  \item Response: We thank the Review for the comment and we moved the original Section 2.3 {\it Time Marching} at the end of Section 3 combining the change based on the comment previously addressed about what to solve for in the proposed algorithm. 
As described in Section 2.2, the repulsion force with a constant strength coefficient $M$ is chosen 
to be a large number in order to avoid particle collisions. If $M$ is not large enough, the hydrophobic attraction will dominate the total force and the dynamics may cause particle collisions with the use of a larger time step. Therefore, with an empirical study to the relationship between 
choices of M and $\gamma$, the parameter set in this work allows the time step to be as large as
$O(10^{-1})$ with no instability. Comparing the time step used in literatures, for instance, in Bystricky {\sl et al.}, {\bf 2020}, Int. J. Numer. Methods Fluids), $\Delta t\sim O(10^{-2})$.
\item Change: We moved Section 2.3 to the end of Section 3 (Section 3.4, page 8, lines 243-248).
\end{itemize}

\noindent
\comment{Section 3: the acronym HAP is not defined in the text.}
\begin{itemize}
  \item Response: Thank you for noticing this oversight. The definition of HAP has
    been added at its first occurrence in Section 3.1. 
  \item Change: This change is in \textcolor{green}{green} (page 5, line 144) since it was also pointed
    out by Reviewer 2.
\end{itemize}

\noindent
\comment{Equation 3.1: use parenthesis to show that the normal
derivative only applies to the Laplace’s Green function $K_0$ and not
the density $\sigma$.}
\begin{itemize}
  \item Change: Parenthesis have been added to equation (3.1).  Equations (3.2) and (3.11) had the same notational issue, and
    they have both been corrected.
\end{itemize}

\noindent
\comment{For clarity, use contraction products ``$\cdot$" when a second
order tensor multiplies a vector to avoid confusion (e.g.~${\bf S} \cdot
{\bf F}$ instead of ${\bf SF}$) in eqs.~(3.4), (3.5), (3.7) and so on
$\ldots$}
\begin{itemize}
  \item Change: This notation has been adjusted throughout Section 3.
\end{itemize}

\noindent
\comment{In practice, how do you compute the derivatives $d\sigma /ds$,
$dv_i/ds$ and $dv_i/d\boldsymbol{\nu}$ in (3.13)?}
\begin{itemize}
  \item Response: Since the only derivatives that are required are functions
    defined only on the boundary of the Janus particles, they are
    computed with spectrally-accurate Fourier differentiation.

  \item Change: We have added the following sentence to the start of Section 3
    \begin{quotation}
      All derivatives are computed with spectrally-accurate Fourier
      differentiation.
    \end{quotation}
\end{itemize}

\noindent
\comment{Line 256: you set the strength of the repulsive force $M = 4k_B
T$. In your simulations there is no thermal fluctuations, so why using
$k_B T$ as a reference energy if it is no there in the simulations?
There should be another energy scale that you could use to calibrate
$M$, right?}
\begin{itemize}
  \item Response: All physical quantities in membrane mechanics such as interfacial tension, bending  modulus, and energy constant in pairwise interactions are defined in units of $k_BT$. 
\end{itemize}

\noindent
\comment{Related question: how much does the interparticle distance
depend on on the strength and range of this artificial repulsive
potential? What is the impact on the vesicle shape and effective
properties?}
\begin{itemize}
  \item Response: We tested the model parameters based on matching simulation results in the previous paper  (Fu {\sl et al.}, {\bf 2020}, Multiscale Model. Simul.). The proposed work adopts a different repulsion force from the previous one and we have done studies in choosing the default parameter set to achieve similar structures. For the effective properties, we leave it as a future work.
\end{itemize}

\noindent
\comment{Figure 3a,b,d: what does the term in parenthesis ``(1)" means
on the label of the ordinate axis?}
\begin{itemize}
  \item Response: The term (1) means the magnitude of the corresponding $y$-axis is of order 1.
\end{itemize}

\noindent
\comment{Line 302: the authors mention that tank-threading can only be
observed for shear rate as high as $10^{6}\text{s}^{-1}$. Can such a
high value be generated in experiments?}
\begin{itemize}
  \item Response: A shear rate of order $10^{6}\text{s}^{-1}$ is too high to be generated in experiments.
Since the size of the JP vesicle in this work is much smaller than experimental use vesicles, 
a very high shear rate of the flow is needed to acquire the tank-treading motion.
\end{itemize}

\noindent
\comment{Eq.~4.4, typo: $v$ should be $u$.}
\begin{itemize}
  \item Change: This typo is fixed.
\end{itemize}

\noindent
\comment{Figure 6: the yellow particle is not visible when printing in
black and white.}
\begin{itemize}
  \item Response: We thank the referee for this comment. We will re-plot all color figures with colorblind friendly colormap if the manuscript should be accepted for publication. We will take this into account as well.
\end{itemize}

\noindent
\comment{Line 388, typo: ``has" should be ``have".}
\begin{itemize}
  \item Change: This typo is corrected.
\end{itemize}

\noindent
\comment{Figure 7a is never referred to and its content is never
discussed in the text.}
\begin{itemize}
  \item Response: Thank you for noticing this missing connection. 
  \item Change: We added a description connected to Figure 7a.
\end{itemize}

\noindent
\comment{Line 393: The reference to panel ``Figure 7c" seems to be a
typo. Same for ``Figures 7c and 7d" on line 394, I think it should be
``Figures 7b and 7c".}
\begin{itemize}
  \item Change: This typo is corrected.
\end{itemize}

\noindent
\comment{Side question: Is it possible to change the vesicle stretching
modulus and hydraulic permeability independently or are these two
properties linked to each other and how?}
\begin{itemize}
  \item Response: We added a parametric study in new Table 2 and the trend provides an idea about 
how to change vesicle stretching modulus and hydraulic permeability by adjusting the length related parameters or force related parameters. We think that it is possible to have better understanding about the link between all parameters and these physical quantities after more 
convergence study.
\item Change: We added a new Table 2 in page 16.
\end{itemize}

### 2022-02-15 doc/reviews/ResponseToReviewer2.tex

\noindent
\comment{The abbreviation HAP is not defined in the text. I guess it stands for hydrophobic attraction potential.
}
\begin{itemize}
  \item Response: Thank you for noticing this oversight. 
  \item Change: The definition of HAP has been added at its first occurrence in Section 3.1. 
\end{itemize}

\noindent
\comment{$u$ is used for both the velocity and the solutions of the
Laplace equation. Please use another variable for the scalar function
$u$.}
\begin{itemize}
  \item Response: The velocity ${\bf u}({\bf x})$ introduced in the mobility problem (eqn. (2.1)--(2.3)) is in bold face and of a vector form. The scalar solution function $u$ is the solution of the screened Laplace equation boundary value problem (eqn. (2.7)--(2.9)). Therefore there is no duplication of usage in notation. 
  \item Change: In response to this point, in order to avoid confusions, we changed the scalar function to $\eta$.
\end{itemize}

\noindent
\comment{$\rho$ used in the HAP is not the same as the one used in the
mobility boundary integral equation. One is a decay length of the
attraction potential, while the second is the Euclidean distance between
two JPs.}
\begin{itemize}
  \item Response: We had used $\rho$ to denote the distance between source and
    target points in one of the layer potentials. This has been removed.

  \item Change: We now use $\rho$ to denote the HAP decay length and $\rho_0$ to
    denote the cutoff for the repulsion force.
\end{itemize}

\noindent
\comment{$\nu$ is used on multiple instances, sometimes as a normal
vector (see line 97 for example), and other times as some scalar
function (see line 203).}
\begin{itemize}
  \item Response: We thank the referee for this oversight.
  \item Change: We now reserve $\boldsymbol{\nu}$ for the normal vector and
    $w_i$ denote the scalar what we previously defined to be $\nu_i$.
\end{itemize}

@@

\noindent
\comment{What is the bending modulus here? I guess that it is not a
direct input parameter in this model but rather a quantity that can be
deduced from other input parameters. If I am right then, what are these
parameters? And could you tune them if needed to simulate the effect of
the membrane stiffness? This can be important in some applications such
as rigidity-based microfluidic sorting devices.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{To compare the results with the existing literature, I would
suggest introducing the capillary number for vesicles as defined in
\url{https://doi.org/10.1016/j.crhy.2009.10.001}.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{For both examples with the linear shear flow and the Poiseuille
flow, the area of the vesicle is not conserved and the relative error
with respect to the stress-free area increases with the increase of the
external stresses. It can reach roughly 7-8\% for the higher shear rate
in the shear flow example. This is quite significant. Do you have a way
to reduce this error to below 1\%? Note that in other numerical models
for vesicles (e.g.~\url{https://doi.org/10.1016/j.jcp.2008.11.036}),
both constant area and perimeter constraints are fulfilled even when the
vesicle is more deformed than the cases reported here.}
\begin{itemize}
  \item Response: We thank the referee for this comment. For impermeable vesicles, the referee is correct about the numerical errors reported in the literature. However, the Janus membrane is permeable and in our simulations we found that the Janus vesicle needs time so the Janus particles in the membrane can re-arrange themselves. During this process of rearrangement the Janus bilayer membrane behaves as a permeable membrane as in Quaife, Gannon and Young (PRF 2021). For a Janus vesicle in a linear shear flow with a shear rate of dimensionless shear $\chi = 0.002$ the enclosed area reaches a nearly constant value after $1$ $\mu$s. We would like to point out that this is not a numerical error, but a consequence of Janus particle hydrodynamics that gives rise to membrane permeability. 
\end{itemize}

\noindent
\comment{In some interesting applications, the fluid encapsulated by the
bilayer membrane has a viscosity which is different from the suspending
fluid. How difficult it is to add this feature to your model?}
\begin{itemize}
  \item Response: Our current numerical method does not support a viscosity contrast in the system 
or the setup similar to the ones in (Veerapaneni {\sl et al.}, {\bf 2011}, Phys. Rev. Lett.),
(Vlahovska and Gracia, {\bf 2007}, Phys. Rev. E), and
(Kaoui and Harting, {\bf 2016}, Rheol Acta). 
As described in the manuscript, the JP vesicle is permeable and the mixture of two different
fluids has to be analyzed within the framework, which would introduce a contact line between fluid 1- JP and fluid 2 -JP boundaries on the Janus particle surface. It is an interesting problem and we plan to study this in the future after we establish some basic knowledge of JP vesicle dynamics in a simpler configuration here.

\end{itemize}

### 2022-02-15 doc/main_jfm.tex

\cite{Brandner2019} used the coarse-grained force field with a lattice
Boltzmann molecular dynamics to simulate the hydrodynamics of a
nano-sized vesicle under a shear flow.  In MD simulations, the
hydrodynamic interactions for the solvent phase are often approximated
by an implicit solvent coarse-grained model.  In the present work, the
hydrodynamic interactions come from the mobility problem for the Stokes
equations for the incompressible, viscous solvent.

We require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but do require solving potentially
expensive nonlinear complementarity problems at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively weak non-stiff repulsive
force.

>>>>

%\cite{Brandner2019} used the coarse-grained force field with a lattice
%Boltzmann molecular dynamics to simulate the hydrodynamics of a
%nano-sized vesicle under a shear flow.  In MD simulations, the
%hydrodynamic interactions for the solvent phase are often approximated
%by an implicit solvent coarse-grained model.  In the present work, the
%hydrodynamic interactions come from the mobility problem for the Stokes
%equations for the incompressible, viscous solvent.

We require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but do require solving potentially
expensive nonlinear complementarity problems at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively \textcolor{red}{soft} repulsive
force \textcolor{red}{(compared to the short-range repulsion that diverges in the Lennard-Jones potential)}.
